%!TEX root = main.tex
\chapter*{Changes}
\begin{description}
\item 14.11.2012 - Worked on \autoref{peacefulBananaApplication} - Peaceful Banana Application. What it does and why use it.
\item 28.11.2012 - Worked on scenarios 1 and 2. Removed scenario 3. 
\item 29.11.2012 - Worked on Literature Review. - Worked on Motivation, Context, Background and Introduction. 
\item 04.12.2012 - Worked on PeacefulBanana chapter and Problem elaboration. Try to state what artifacts the tool work with, what process models it can be used with, Github commitment. Added some TODO in Problem elaboration(reflection aspects, long term objectives etc. )
\item 13.12.2012 - Updated Scenarios in Problem elaboration chapter. 
\item 20.12.2013 - Updated report for christmas break
\item 20-27.01.2013 - Worked on testplan for usability test, to be included in report. 
\item 29-30.01.2013 - Updated scenarios with screenshots from a user's perspective. Also replaced some old screenshots. 
\item 18.02.2013 - Updated Implementation (not completed yet)
\item 19.02.2013 - Added table of figures, added domain diagram and completed the description of the database.
\item 20.02.2013 - Created quickstart chapter and changes to peacefulbanana chapter.
\item 04.03.2013 - Much work done on quickstart, basically done only need one more screenshot. 
\item 11.03.2013 - Quickstart is finished. Much work on design chapter. 
\item 13.03.2013 - Work on literature review/state of the art. Wrote about some similar tools for agile development that integrates with Github.
\item 13-20.03.13 - Revised quickstart, added background chapter, more literature background and design chapter has been added. 
\end{description}