%!TEX root = main.tex
\chapter{Introduction}
This thesis presents a design-science project where the goal was to design a web tool for use as support for learning and reflection in agile project development teams. The tool was given the name \emph{PeacefulBanana} and the name has since remained unchanged. The purpose of the tool is to make collection of experiences easier during a project development process, and enhance learning outcomes from the reflection sessions. 
The tool collects data from the development process and presents them to the users in a tailored way. Users can annotate these data with their own experiences, including connecting feelings to these experiences. The application presents these data and experiences for use in both individual and collaborative reflection settings. The challenge will be to collect, annotate and present the data in a way that helps the learner to understand what they have experienced and learn from these experiences. That is helping them reflect on the experiences made and learn from them. Boud et.al\citep{boudreflection1985} presents that; \emph{reflection is a process where the experience is revisited, feelings are re-attended and the experience is re-evaluated}. This means that it is important to tailor reflection in order to support and achieve learning from experiences. Using technology to collect data and experiences from everyday work, and the potential for using this to support reflection has been shown to be growing \citep{li2011understanding}. In this thesis we utilize technology for reflection, by trying to capture everyday data related to work experiences, make them available for reflection and store them for later use. The quality of data collected will have an impact on how easy it is for users to revisit the experience and reflect upon it. By using technology we hope to make the challenge of capturing the experience with it's ideas and feelings to support the reflective process easier to overcome. 

\section{Context \& Domain}
For many years now, agile methods in software development have been widely used in software development teams. Agile methodologies are software development methods that is based on iterative and incremental development. This means that requirements and solutions are dynamic and comes as a result of collaboration between self-organizing teams. Agile methods focuses on adaptive planning, iterative development and encourages teams to respond to changes in a flexible way. The agile manifesto presents a principle which states that an agile team should regularly reflect on how to become more effective, and tune its behavior accordingly\citep{Beck2001}. Continuously improving through introspection is a vital part of agile methods and is applied in f.ex retrospectives\citep{Beck1999, Derby2006, Maham2008}. Cockburn impose that a vital part of agile practice should be conducting regular retrospective workshops aimed at reflection and process tune-up\citep{Cockburn2006}. Agile methods focus on continuous iterations repeating the same development steps, and thus progressing. Retrospectives in agile development processes are most often performed after each iteration. This is done by gathering the team and reflecting on their way of working, so that improvements for the next iteration can be identified \citep{Derby2006, Drury2011}. This enables agile self-governing teams to react quickly to changes, and make modifications accordingly\citep{Drury2011}. Retrospectives could also support communication and interaction within the team, which is important for agile development. \\ 
There are however shortcomings of applying retrospectives in agile teams. Agile teams tend to focus primarily on short-term issues that were identified for a single iteration, and not on long-term strategic issues\citep{Drury2011}. Reflection on work related experiences enables users to reflect and derive conclusions from the reflection \citep{Korthagen_Vasalos_2005}. This turns experiences into knowledge that can be applied to the everyday challenges of work. This creates an individual aspect, where the reflection on previous work can be applied to future work challenges. In addition to this individual aspect, reflection has been shown to have strong social aspects, and is often accomplished collaboratively between users in such agile teams \citep{Høyrup_2004}. Therefore a challenge will be to easily allow users to identify their common tasks and shared work experiences. In software development projects in the industry, it is often a challenge for teams to prioritize retrospectives, as there is other work that is seen as more important \citep{kasi2008post}. For students, revisiting experiences and reflecting on these is often seen as unnecessary and in the way of other tasks, like writing code, testing or documentation. Another challenge is collecting data of sufficient quality to support this reflection, and also how to share this data, experiences and reflection with the rest of the team.  

In this thesis we developed a tool in order to address the challenges of collecting data of sufficient quality to support reflection, and how to share this data and experiences so experiences are available for revisiting and reflection can occur. We wish to allow teams to not only reflect on experiences for the last period of the iteration, but also allow users to go back in time several iterations, in order to identify long-term issues and trends within the team. The tool is aimed at supporting reflection by scaffolding the collection of relevant project artifacts, and prompting users to annotate these artifacts with their experiences and feelings. The tool is designed and developed for software development projects using an agile method, and will be evaluated with a usability study, a focus group consisting of software developers and also an expert in the field of agile methodologies. 

\subsection{Core Concepts}
In this section we will look at some of the concepts for this thesis and what the application builds upon. The concepts are areas that needs introduction in order to gain understanding of the thesis and its theoretical background.

\subsubsection{Reflection}
The goal is to offer technology that not only makes information search and collection efficient, but also support reflection in a collaborative session. Through reflection learning can be achieved and users can collaborate on gathering information for experiences and the ability to reflect over experiences by displaying data in different methods this might enhance the reflection ability and letting the user view data in another way.

\subsubsection{Learning from experience}
According to David Kolb\citep{KolbModel} for a learning experience to occur there must exists certain abilities in the learner. First the learner must be willing to actively be involved in the experience Secondly the learner must be able to reflect on the experience and third, the learner must possess and be able to use analytical skills to conceptualize the experience. And last the learner must posses decision making and problem solving skills to be able to create new knowledge outcomes based on the experience.
% Se på timeline, de har mye gode kilder her

\subsubsection{Software development}
% Trekke inn modellen til birgit? YES!
Software developers generate a lot of data when developing software, when committing data to version control systems or closing tasks and issues in a project management tool. During a agile development cycle, tasks is distributed among the developers and they make decisions either individually or in plural. Normally this data is never looked at again, but they contain vital information on choices the developers make on a daily basis. It is important to make collecting of information a part of developers normal day-to-day activities based on the model from \citep{Krogstie2009}.

\subsubsection{Version-control systems}
Version-control system is the management of changes to documents, source files or other collections of information. These artifacts are usually identified by a 'revision'\footnote{An unique identifier normally a number or string.}, when creating a revision a lot of data is stored together with the revisioned files. Like who committed the data, when it was committed and what files that where affected by the change.

In software development version-control systems can be used for documentation and configuration files as well as source code. As teams develop software, it is common for different versions to be create and developers to work at the same time, sometimes in the same files. Different version can be tagged in the version-control system, so it is easy to back in time to that state where the tag for a stable version was created.

\include{ResearchQuestion}
\include{ResearchMetod}
\section{Outline}
% Muligens ha mer utfyllende info i hvert kap, mer om hva som skjer der
In this section we will describe the organization of the remaining chapters in our thesis. 
\\*
\\*
\textbf{Chapter 2} gives a general overview of the PeacefulBanana application. The intention is to present features and concepts of the application on an abstract level.
\\*
\\*
\textbf{Chapter 3} describes the theoretical background behind over thesis, including reflection, experiences and experience based learning. 
\\*
\\*
\textbf{Chapter 4} describes our State-of-the-art, the literature review that was performed and related work. The chapter presents some of the work performed in the domains of technology for reflection and experience based learning, with related work acting as a basis for our own implementation of technology. 
\\*
\\*
\textbf{Chapter 5} presents the problem definition, user stories and our scenarios. 
\\*
\\*
\textbf{Chapter 6} describes the requirements chapter, elaborated from problem elaboration and the scenarios. 
\\*
\\*
\textbf{Chapter 7} describes the design choices behind the creation of the PeacefulBanana tool.
\\*
\\*
\textbf{Chapter 8} describes how we implemented the PeacefulBanana tool. 
\\*
\\*
\textbf{Chapter 9} includes a description of the testing we have performed before and during implementation of the tool. 
\\*
\\*
\textbf{Chapter 10} includes a description of the final evaluation of the application, performed with a focus group consisting of students taking the IT2901 course at NTNU together and an evaluation with an expert in the field of agile software development. The chapter also features a discussion of the results gathered compared to our research questions. 
\\*
\\*
The last chapter of our thesis, is a conclusion with a summary, our research contributions, an evaluation of our work and ideas towards future work.