\chapter{Problem Elaboration}
\label{problemelaboration}
In this chapter we will elaborate our problem by defining our task and presenting our high level requirements.
This chapter describes in more details the problem that you are addressing and that
has been briefly outlined in the Introduction. This chapter might contain scenarios that
illustrate the problem and help identifying requirements.

\section{Problem Definition}
\label{problemdefinition}

To answer our research questions we will develop a web-tool that allow users to create, share and reflect upon agile project experiences annotated with data relevant for reflection. 
The experiences will be presented in several different ways like graphs and tagclouds. The tool will be designed with reflection in mind, but the tool will also function as 
a tool that fits several scenarios and can be used by different groups of users. 

\section{Reflection and technology}
The world wide web and modern technologies provides easy access to enormous amounts of information. This means that in order to learn, learners must be able to make sense of the information collected.  
In order to achieve this and make conscious decisions of how to use information, learners need to reflect on the information they collect. Reflection upon the process of solving problems is necessary to achieve a good result and to improve the ability to learn from experiences. When supporting learning with technology, this technology should promote these aspects within learning\cite{Lin1999}

The main goal is to provide technology that enables efficient information retrieval, and to provide scaffolds that support reflective thinking and problem solving. In our task this means utilizing collaborative learning experiences. 

\section{Scenarios}
\label{problemdefinition}
Based on related work, we have developed three scenarios to show what we want our tool to support in terms of collaborative reflection and learning. These three scenarios will provide a basis for the requirement elaboration and design choices in development of the tool. 
\\
At the Norwegian University of Science and Technology, NTNU, a group of students are taking the course IT2901 - Informatics Project II\footnotemark.
In the course, the focus is not only on the project itself, but also on the process the group steps through in order to reach their goal, including group roles, distribution of work etc. At the end of the course, students have to present a product report, with their project results, and a process report, with their project process results and experiences. In addition to this, groups participate in a retrospective workshop at the end of the course. In these three scenarios, our users are students and part of a group in the course , with age ranging from 22 and up to 28 years old.
\\
The group is going to work on a customer-driven project, using an agile methodic like scrum. The group will be using Github as a versioning-control system. During the project work the team will use Github to collect information. The PeacefulBanana tool can then be used to gather this information and present it in a scaffolded way mainly to be used in reflection sessions. Users can though, at any time go into the application and gather relevant data if they want to. This data will help the group to see trending issues and problems they have come upon in the process. Each member of the group will register as a user on the PeacefulBanana tool. The users will then be connected together as a group. 
\\
The three scenarios described in the next sections provides examples of how we envision the usage of the PeacefulBanana tool in three different settings. First as a retrospective in the end of each iteration, then as a part of a workshop at the end of the course, and finally as a reflection session across teams - in order to learn from different projects. 
The two first scenarios were developed early in the development process. The first scenario features using the tool as part of the agile methodic 'Scrum', where in the end of each iteration there is a retrospective reflection session. The second scenario shows usage of the tool as part of the mentioned retrospective workshop at the end of the course. The third scenario were developed a bit later, as we wanted to show how the tool can promote reflection across teams. 
\\

\footnotetext{Informatics Project II is a course where students from the Informatics education program is put together in groups working on different software development projects. Key objectives of this course are gaining practical experience in GROUP-ORIENTED software engineering for a customer, covering the whole life-cycle of a software project - \url{http://www.ntnu.edu/studies/courses/IT2901}}

\subsection{Scenario 1}
\label{scenario1}

Using the tool as part of the agile methodic ‘Scrums’ retrospective-reflection meetings reflecting upon the last week/2weeks or what the iteration duration might be.  The tool will provide users with the option of generating a report/graphs/other data that can be used to remember certain situations and how the group/persons dealt with this matter. The team will be able to generate tagclouds from commit messages during an iteration to see what issues or ‘tags’ were the most common for that period. This enables the team to reflect on the different issues. 

\subsection{Scenario 2}
\label{scenario2}
Using the tool as part of the course final workshop, reflecting on the project process as a whole. 
This scenario uses the tool to indicate how the project has been long-term. What issues are common over several milestones(tagclouds), graphs etc. Also possibly mood-trajectories both personal and as a group. The tool will enable a group to see the whole project course more clearly, but also be able to dive into certain issues or milestones that showed to be of particular interest, which in turn can aid reflection. 

\subsection{Scenario 3}
\label{scenario3}
for use for later reflection: Using the tool daily as a personal tool making relevant notes and other relevant things like feelings in order to reflect upon this later. Project members use github daily for commits, comments and as a general version-control and issue-tracker tool. By integrating the github data with our tool, project members could see commits made, milestones reached etc. and take notes regarding these events. Other functions is adding relevant tags, emotions and such. Using the tool daily means all the notes, emotions etc. are fresh and correct. Later in the retrospectives mentioned in scenario 1 and 2 , members can look back and remember emotions and what actually went on. This leads to better reflection, as it has been shown that memories change over time, so inputting the fresh experiences for later use is important. 
