%!TEX root = main.tex
\chapter{Functional Requirements}
\label{cha:funcreq}
In this chapter both functional and non-functional requirements the application should meet, in order to better support elaboration and implementation of the final application. 
The requirements detailed in this chapter are prioritized according to how important they are for the implementation, with a three step scale. 

\vspace{0.5cm}
\begin{itemize}
    \item[\textbf{H}]{High-priority requirements must be met by the application.} 
    \item[\textbf{M}]{Medium-priority requirements should be met by the application, but omission will severely limit the application.}
    \item[\textbf{L}]{Low-priority requirements is not vital to the application, but should be met if all high and medium requirements are met.}
\end{itemize}
\vspace{0.5cm}

For this thesis, a three step scale gives us adequate data for decisions without sacrificing too much fidelity.
In addition to prioritizing the requirements based on importance, the requirements will also be prioritized according to how hard and time consuming they are to implement. These priorities will use the H-M-L scale as described below. 

\vspace{0.5cm}
\begin{itemize}
    \item[\textbf{H}]{High is something that will take more than 10 hours to implement.}
    \item[\textbf{M}]{Medium is something that will take between 5 and 10 hours to implement.}
    \item[\textbf{L}]{Low is something that will take less than 5 hours to implement.}
\end{itemize}
\vspace{0.5cm}
Annotating requirements with both importance and difficulty priorities provides a a way to perform a \emph{cost/benefit} analysis for each of the requirements. A cost/benefit analysis is a way of weighing the total value of benefits against the costs of implementing them\cite{cellini2010cost}.
\begin{equation}
Net Benefits = Total Benefits - Total Cost
\end{equation}
A requirement that is hard to implement fully, but is of little importance to the project as a whole could be dropped in benefit for a more important one (or a less difficult one), if time and/or costs involved are deemed to be to large.

\subsubsection{General Requirements}
\begin{itemize}
    \vspace{0.5cm}
	\item[\textbf{FR1}] Users must be able to register a new account. \\
        \textit{\small{An account is necessary in order to use the application. }}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential \\
            Difficulty & \textbf{M} - Implementation-time 5-10 hours\\
            \hline
        \end{tabular}
    \vspace{0.5cm}
    \item[\textbf{FR2}] Users must be able to log in \\
        \textit{\small{An active session is necessary in order to present user-specific data}}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential \\
            Difficulty & \textbf{M} - Implementation-time 5-10 hours \\
            \hline
        \end{tabular}
    \vspace{0.5cm}

    \subsubsection{GitHub Requirements}
    \item[\textbf{GR1}] GitHub account authorization\\
        \textit{\small{The application should be able to authorize the application with users GitHub account}}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential. Users need to allow the application to access data from their GitHub repositories\\
            Difficulty & \textbf{H} - Could be very time consuming, 10-20 hours \\
            \hline
        \end{tabular}
    \vspace{0.5cm}

    \item[\textbf{GR2}] GitHub Synchronization\\
        \textit{\small{The application should be able to synchronize with GitHub whenever there is a new event or commit in one of the user's repositories.}}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential. Synchronization is important in order to present the newest data to the users\\
            Difficulty & \textbf{H} - Major functionality. 20-30 hours\\
            \hline
        \end{tabular}
    \vspace{0.5cm}

    \subsubsection{Server Requirements}
    \item[\textbf{SR1}] Persistent Storage\\
        \textit{\small{Create MySQL database support for creating and performing actions on persistent databases by the application}}
        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential - Persistent storage is vital for the application to collect and store data\\
            Difficulty & \textbf{M} - Moderately time consuming. 5-10 hours\\
            \hline
        \end{tabular}
    \vspace{0.5cm}

    \item[\textbf{SR2}] Databases\\
        \textit{\small{Create databases for different functionality: users, reflection notes,commits, milestones, repositories, etc}}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential for functionality that requires synchronization with database\\
            Difficulty & \textbf{M} - Moderately time-consuming. 8-10 hours\\
            \hline
        \end{tabular}
    \vspace{0.5cm}

    \item[\textbf{SR3}] Domain Classes\\
        \textit{\small{Create domain classes for the relation database}}

        \begin{tabular}{| l | p{7cm} |}
            \hline
            \rowcolor[gray]{0.8}
            \textbf{Impact} & \textbf{Values} \\
            \hline
            Importance priority & \textbf{H} - Essential for all entities and their relations in the database \\
            Difficulty & \textbf{H} - Could be very time consuming, 10+ hours \\
            \hline
        \end{tabular}
    \vspace{0.5cm}